Social Participation Ontology: community documentation, enhancements and use examples

### 2015-01-12 paper.tex
arrumacoes de bibliografica, escrita e inclusao do Dilvan a Karina

%\author{Flor Karina Mamani Amanqui}
%  \homepage{http://java.icmc.usp.br}
%  \email{florkarina27@gmail.com}
% \altaffiliation{Instituto de Ci\^encias Matemáticas e de Computação (ICMC/USP)}%Lines break automatically or can be forced with \\
%
%
%
%\author{Dilvan A. Moreira}
%  \homepage{http://java.icmc.usp.br}
%  \email{dilvan@icmc.usp.br}
% \altaffiliation[also at ]{(ICMC/USP)}%Lines break automatically or can be forced with \\

@@

\begin{acknowledgments}
This article is deeply influenced by Protege and BFO documentation. Authors thank community and researchers related to these projects~\cite{protege,bfo}.
Authors thank \corais\ Platform maintainers for their efforts in delivering a collaborative platform which gave birth to \vcps\ documentation. Authors thanks Prof. Dr. Dilvan de Abreu Moreira (ICMC/USP) for all help and incentives in the genesis of this article. Authors thank Flor Karina Mamani Amanqui for initial Spanish labels.
Renato Fabbri is grateful to CNPq (process 140860/2013-4, project 870336/1997-5), PNUD/ONU (contract 2013/00056, project BRA/12/018), SNAS/SG-PR, and the Postgraduate Committee of the IFSC/USP. 
% 2013/00056, projeto BRA/12/018 (pelo que?? nao me lembro mais e nao anotamos)
\end{acknowledgments}

>>>>

\author{Flor Karina Mamani Amanqui}
  \homepage{http://java.icmc.usp.br}
  \email{florkarina27@gmail.com}
  \altaffiliation{Instituto de Ci\^encias Matem\'aticas e de Computa\c{c}\~ao (ICMC/USP)}%Lines break automatically or can be forced with \\

\author{Dilvan A. Moreira}
  \homepage{http://java.icmc.usp.br}
  \email{dilvan@icmc.usp.br}
 \altaffiliation[also at ]{(ICMC/USP)}%Lines break automatically or can be forced with \\

@@

\begin{acknowledgments}
This article is deeply influenced by Protege and BFO documentation. Authors thank community and researchers related to these projects~\cite{protege,bfo}.
Authors thank \corais\ Platform maintainers for their efforts in delivering a collaborative platform which gave birth to \vcps\ documentation.
Renato Fabbri is grateful to CNPq (process 140860/2013-4, project 870336/1997-5), PNUD/ONU (contract 2013/00056, project BRA/12/018), SNAS/SG-PR, and the Postgraduate Committee of the IFSC/USP. 
% Authors thanks Prof. Dr. Dilvan de Abreu Moreira (ICMC/USP) for all help and incentives in the genesis of this article. Authors thank Flor Karina Mamani Amanqui for initial Spanish labels.
\end{acknowledgments}
